Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-16 VMCAI-revised-version/final.tex
up

\begin{theorem}\cite{DBLP:journals/lmcs/BlondinFM17}
Coverability is decidable for any ideally-effective WBTS.
\end{theorem}

@@

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}\label{ref ozkan}
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for effective $\post^*$-basis WSTS with strong compatibility
when
$\Safe=\uparrow \Safe$.
\end{theorem}

>>>>

\begin{theorem}(Blondin~\cite{DBLP:journals/lmcs/BlondinFM17})
Coverability is decidable for any ideally-effective WBTS.
\end{theorem}

@@

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
\begin{theorem}\label{ref ozkan}
(\"Ozkan~\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889})
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for effective $\post^*$-basis WSTS with strong compatibility
when
$\Safe=\uparrow \Safe$.
\end{theorem}
